\documentclass[12pt, a4paper, twoside, openright]{report}

% ===========================================================
% ======================== packages =========================
% ===========================================================
\usepackage[ngerman, english]{babel}
\usepackage[ansinew]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2cm]{geometry}
\usepackage[onehalfspacing]{setspace}
\usepackage[section]{placeins} %Bilder rutschen nicht aus section
\usepackage[markup=nocolor,deletedmarkup=xout]{changes}
\usepackage{cancel}			%MET symbol
\usepackage{chngcntr}
\usepackage{lscape}
\usepackage[normal]{caption} %style für Bildunterschriften
\usepackage{multicol} 
\usepackage{epstopdf}		%.eps get converted to pdf
\usepackage{textcomp}
\usepackage{url}			%for hyperlinks
\usepackage{blindtext} 		%use blindtext
\usepackage{subcaption} 	%for (a) in subfigures
\usepackage{tikz} 			%new graphic options
\usepackage{verbatim}		
\usepackage{microtype} 		%bessere Zeilenumbrueche, z.B. ISBN in Literatur
\usepackage{typearea}
\usepackage{tikz-feynman} 	%Feynman Diagrams
\tikzfeynmanset{compat=1.1.0}
\usepackage{fancyhdr}		%new head and foot lines
\usepackage[babel, german=quotes]{csquotes}
\usepackage{hyperref}
%\usepackage[style=lucas_unsrt, maxbibnames=100, sorting=none, backend=bibtex]{biblatex}
%\usepackage{biblatex}
\usepackage{bibgerm}
\bibliographystyle{lucas_unsrt}
% ===========================================================
% ======================== new commands =====================
% ===========================================================
\newcommand*\chem[1]{\ensuremath{\mathrm{#1}}} %chem formulas

% ===========================================================
% ======================== configuration ====================
% ===========================================================
% customised header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[CE,CO]{\thepage}
\fancyhead[CO]{\rightmark}
\fancyhead[CE]{\leftmark}
% redefine cleardoublepage: do not print fancy headline if page is empty before new chapter
\let\mtcleardoublepage\cleardoublepage
\renewcommand{\cleardoublepage}{\clearpage{\pagestyle{empty}\mtcleardoublepage}}
% =======================
% title style
\usepackage{color}
\definecolor{gray75}{gray}{0.75}
\usepackage{titlesec}
\titleformat{\chapter}[block]
  {\normalfont\Huge\bfseries}
  {\thechapter \hspace{20pt} \textcolor{gray75}{|} \hspace{20pt}}
  {0pt}
  {\Huge}
\titlespacing*{\chapter}{0pt}{0cm}{1cm}
\titleformat{\section}[block]
  {\normalfont\Large\bfseries}
  {\thesection}
  {1em}
  {}
\titleformat{\subsection}[block]
  {\normalfont\large\bfseries}
  {\thesubsection}
  {1em}
  {}
\titleformat{\subsubsection}[block]
  {\normalfont\normalsize\bfseries}
  {}
  {1em}
  {}
% =======================           
% let figure, tables, etc stay in chapter
\counterwithin{figure}{chapter}
\counterwithin{table}{chapter}
\counterwithin{equation}{chapter}
% ======================= 
% bibliography stuff
%\addbibresource{MasterBib.bib}
%\ExecuteBibliographyOptions{% 
%firstinits=true, 
%maxbibnames=3, % Alle Autoren (kein et al.) 
%minalphanames=3, 
%maxalphanames=3, 
%}% 


\urlstyle{same}
% =======================
\begin{document}
% ===========================================================
% ======================== Deckblatt ========================
% ===========================================================
\selectlanguage{ngerman}
\pagenumbering{roman}
\thispagestyle{empty}
\include{Titlepage}
% clearpage without page number:
{\clearpage{\pagestyle{empty}\mtcleardoublepage}} 
%Abstract
\section*{Zusammenfassung}
\thispagestyle{plain}

\selectlanguage{english}
\section*{Abstract}
The presented analysis aims at a measurement of the jet mass distribution in collimated full hadronic top quark decays, where the top quark is reconstructed within one single jet. The jet mass is sensitive to the top quark mass and therefore an essential jet substructure variable for top quark identification. Understanding jet substructure is essential in future analyses with LHC data, because as a consequence of the high centre-of-mass energy, heavy objects are often Lorentz boosted and have to be identified with a single jet. Studies with various jet clustering algorithms are presented to find the most suitable method to reconstruct the jet mass in top quark decays. Consequently, the exclusive jet clustering algorithm XCone shows the best performance and is used to obtain a jet mass distribution that is unfolded to particle level. The unfolding is applied to be able to compare with analytical calculations. Furthermore, the top quark mass can be extracted without relying on Monte Carlo simulations. Proving the method of this analysis, an unfolded jet mass distribution is presented as result. The measurement is performed in the $t\bar{t}$ enriched region, where the one of the top quarks is required to decay in the lepton+jet channel. This offers a good suppression of non-$t\bar{t}$ backgrounds while retaining a high selection efficiency. For this analysis, data recorded by the CMS detector in 2016 at a centre-of-mass energy of $13\;\text{TeV}$, corresponding to an integrated luminosity of $37.76\;\text{fb}^{-1}$, is used.


\clearpage
\tableofcontents
\addtocontents{toc}{~\hfill\textbf{Page}\par}
\clearpage
{\pagestyle{empty} \cleardoublepage}



\pagenumbering{arabic}
\selectlanguage{english}
% ===========================================================
% ======================== Inhalt ===========================
% ===========================================================
%todo Absaetze, indent pruefen
\include{Introduction}
\include{Theory}
\include{Measurement_Boosted}
\include{Experiment}
\include{Reconstruction}
\include{Data_MC}
\include{Analysis}
\include{Summary}
\include{Appendix}
\pagestyle{plain}
% ===========================================================
% ======================== Literaturverzeichnis =============
% ===========================================================
% Einträge erscheinen nur, wenn sie auch zitiert werden!!!
%\printbibliography
\bibliography{MasterBib}

%todo in bib style formatieren. z.B. darf "CMS Collaboration" nicht C. Collaboration werden
%----------------------------------------------------------------
%------------------Unterschrift----------------------------------
%----------------------------------------------------------------
\selectlanguage{ngerman}
\cleardoublepage
%todo einverstanden/nicht einverstanden??
\noindent Hiermit bestätige ich, dass die vorliegende Arbeit von mir selbstst"andig verfasst wurde und ich keine anderen als die angegebenen Hilfsmittel -- insbesondere keine im Quellenverzeichnis nicht benannten Internet-Quellen -- benutzt habe und die Arbeit von mir vorher nicht einem anderen Prüfungsverfahren eingereicht wurde. Die eingereichte schriftliche Fassung entspricht der auf dem elektronischen Speichermedium. Ich bin damit einverstanden, dass die Masterarbeit veröffentlicht wird.\\
\newline
\newline
\newline
\begin{tabular*}{\textwidth}{lll}
	\hline
	Ort, Datum & \hspace{10.4cm} & Unterschrift  \\
\end{tabular*}

\cleardoublepage
%----------------------------------------------------------------
%---------------------Danksagung---------------------------------
%----------------------------------------------------------------
\section*{Danksagung}
Zun"achst m"ochte ich Prof. Dr. Johannes Haller daf"ur danken, dass ich die M"oglichkeit hatte, meine Masterarbeit in seiner Forschungsgruppe "uber dieses interessante Thema zu schreiben. Desweiteren bedanke ich mich f"ur die vielen R"ucksprachen und Denkanst"o"se, die meine Arbeit stets bereichert haben. Prof. Dr. Peter Schleper m"ochte ich daf"ur danken, dass er das Zweitgutachten meiner Arbeit "ubernehnommen hat. Ein besonderer Dank gilt Dr. Roman Kogler, der viel Zeit in die Betreuung meiner Analyse, zahlreiche Diskussionen "uber Jets und die Korrektur meiner Arbeit gesteckt hat. Au"serdem danke ich allen Mitgliedern der Arbeitsgruppe und insbesondere meinen B"uronachbarinnen und -nachbarn f"ur die Menge an gekl"arten Fragen, eine nette Atmosph"are und erhellende Gespr"ache in und abseits der Teilchenphysik. Zuletzt m"ochte ich meiner Familie und vor allem Inga danken, die mich immer unterst"utzt haben. 

\end{document}  
%----------------------------------------------------------------
%----------------------------------------------------------------
%----------------------------------------------------------------
